\documentclass[11pt, a4paper, leqno]{article}
\usepackage{a4wide}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{float, afterpage, rotating, graphicx}
\usepackage{epstopdf}
\usepackage{longtable, booktabs, tabularx}
\usepackage{fancyvrb, moreverb, relsize}
\usepackage{eurosym, calc}
% \usepackage{chngcntr}
\usepackage{amsmath, amssymb, amsfonts, amsthm, bm}
\usepackage{caption}
\usepackage{mdwlist}
\usepackage{xfrac}
\usepackage{setspace}
\usepackage[dvipsnames]{xcolor}
\usepackage{subcaption}
\usepackage{minibox}
% \usepackage{pdf14} % Enable for Manuscriptcentral -- can't handle pdf 1.5
% \usepackage{endfloat} % Enable to move tables / figures to the end. Useful for some
% submissions.

\usepackage[unicode=true]{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    anchorcolor=black,
    citecolor=NavyBlue,
    filecolor=black,
    menucolor=black,
    runcolor=black,
    urlcolor=NavyBlue
}


\widowpenalty=10000
\clubpenalty=10000

\setlength{\parskip}{1ex}
\setlength{\parindent}{0ex}
\setstretch{1.5}


\begin{document}

\title{Reproduction and Expansion of \\"SPECIALIZATION TRENDS IN ECONOMICS RESEARCH" by Sebastian Galiani, Ramiro H. Gálvez, and Ian Nachman}

\author{Felix Schmitz}

\date{
    {\bf Under construction}
    \\[1ex]
    \today
}

\maketitle
\footnotetext[1]{Email: \href{mailto:s87fschm@uni-bonn.de}{s87fschm@uni-bonn.de}}

\begin{abstract}
    Some abstract here.
\end{abstract}

\clearpage

There are 6 digits in the current range without a corresponding discussion paper accessible.
The numbers are (4953, 12119, 12315, 12577, 12664, 16580).
The first discussion paper would have been from May 2010.
The later five ones fall into the time span January 2019 to November 2023.

There are 9 discussion paper entries without a corresponding discussion paper file accessible.
The numbers are (9, 18, 21, 28, 33, 56, 173, 16801, 17143).
The first nine fall into the range June 1998 to July 2000.
The later two are from February and July 2024.

These 15 entries are excluded from the analysis.

\clearpage

\end{document}
